---
title: "Correct Response Plots: Clinicians vs Students"
author: "Spiro Stilianoudakis"
date: "April 25, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(openxlsx)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(reshape2)
```

#Setting Working Directory

```{r}
setwd("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Asymmetry")
```

# Loading Clinician Dataset (complete cases)

```{r}
cliniciandata_comp <- readRDS("cliniciandata_comp.rds")
```

# Loading Student Dataset (complete cases)

```{r}
studentdata_comp <- readRDS("studentdata_comp.rds")
```


## Creating long form data with correct response rates

###Clinicians

```{r}
clinician_response <- data.frame(male_sym.factor = sum(cliniciandata_comp$male_sym.factor=="No")/length(cliniciandata_comp$male_sym.factor),
                                 male_1mm.factor = sum(cliniciandata_comp$male_1mm.factor=="Yes")/length(cliniciandata_comp$male_1mm.factor),
                                 male_1.5mm.factor = sum(cliniciandata_comp$male_15mm.factor=="Yes")/length(cliniciandata_comp$male_15mm.factor),
                                 male_2mm.factor = sum(cliniciandata_comp$male_2mm.factor=="Yes")/length(cliniciandata_comp$male_2mm.factor),
                                 male_2.5mm.factor = sum(cliniciandata_comp$male_25mm.factor=="Yes")/length(cliniciandata_comp$male_25mm.factor),
                                 male_3mm.factor = sum(cliniciandata_comp$male_3mm.factor=="Yes")/length(cliniciandata_comp$male_3mm.factor),
                                 male_3.5mm.factor = sum(cliniciandata_comp$male_35mm.factor=="Yes")/length(cliniciandata_comp$male_35mm.factor),
                                 male_4mm.factor = sum(cliniciandata_comp$male_4mm.factor=="Yes")/length(cliniciandata_comp$male_4mm.factor),
                                 
                                 female_sym.factor = sum(cliniciandata_comp$female_symm.factor=="No")/length(cliniciandata_comp$female_symm.factor),
                                 female_1mm.factor = sum(cliniciandata_comp$female_1mm.factor=="Yes")/length(cliniciandata_comp$female_1mm.factor),
                                 female_1.5mm.factor = sum(cliniciandata_comp$female_15mm.factor=="Yes")/length(cliniciandata_comp$female_15mm.factor),
                                 female_2mm.factor = sum(cliniciandata_comp$female_2mm.factor=="Yes")/length(cliniciandata_comp$female_2mm.factor),
                                 female_2.5mm.factor = sum(cliniciandata_comp$female_25.factor=="Yes")/length(cliniciandata_comp$female_25.factor),
                                 female_3mm.factor = sum(cliniciandata_comp$female_3mm.factor=="Yes")/length(cliniciandata_comp$female_3mm.factor),
                                 female_3.5mm.factor = sum(cliniciandata_comp$female_35mm.factor=="Yes")/length(cliniciandata_comp$female_35mm.factor),
                                 female_4mm.factor = sum(cliniciandata_comp$female_4mm.factor=="Yes")/length(cliniciandata_comp$female_4mm.factor))
                                 
              
clinician_long <- melt(clinician_response)                
clinician_long$Respondent <- "Clinician"
clinician_long$Asymmetry <- rep(c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"), 2)
clinician_long$Asymmetry <- factor(clinician_long$Asymmetry, levels = c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"))
clinician_long$Image_gender <- c(rep("Male", 8), rep("Female", 8))
clinician_long$Image_gender <- factor(clinician_long$Image_gender, levels = c("Male", "Female"))


```

### Proportion test for baseline

```{r}
prop.test(c(168,114),c(173,123))
prop.test(c(168,114),c(173,123), alternative = "less")
```


####Oral and Maxillofacial Surgery vs Orthodontist

```{r}
clinician_specific_response <- data.frame(#Oral and Maxillofacial Surgery
								 ##Male photo
								 male_sym.factor.oms = sum(cliniciandata_comp$male_sym.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="No")/length(cliniciandata_comp$male_sym.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_1mm.factor.oms = sum(cliniciandata_comp$male_1mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_1mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_1.5mm.factor.oms = sum(cliniciandata_comp$male_15mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_15mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_2mm.factor.oms = sum(cliniciandata_comp$male_2mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_2mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_2.5mm.factor.oms = sum(cliniciandata_comp$male_25mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_25mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_3mm.factor.oms = sum(cliniciandata_comp$male_3mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_3mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_3.5mm.factor.oms = sum(cliniciandata_comp$male_35mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_35mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 male_4mm.factor.oms = sum(cliniciandata_comp$male_4mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_4mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 
								 ##Female photo
                                 female_sym.factor.oms = sum(cliniciandata_comp$female_symm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="No")/length(cliniciandata_comp$female_symm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_1mm.factor.oms = sum(cliniciandata_comp$female_1mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_1mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_1.5mm.factor.oms = sum(cliniciandata_comp$female_15mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_15mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_2mm.factor.oms = sum(cliniciandata_comp$female_2mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_2mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_2.5mm.factor.oms = sum(cliniciandata_comp$female_25.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_25.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_3mm.factor.oms = sum(cliniciandata_comp$female_3mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_3mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_3.5mm.factor.oms = sum(cliniciandata_comp$female_35mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_35mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
                                 female_4mm.factor.oms = sum(cliniciandata_comp$female_4mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_4mm.factor[cliniciandata_comp$specialty.factor=="Oral and Maxillofacial Surgery"]),
								 
								 #Orthodontist
								 ##Male photo
								 male_sym.factor.or = sum(cliniciandata_comp$male_sym.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="No")/length(cliniciandata_comp$male_sym.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_1mm.factor.or = sum(cliniciandata_comp$male_1mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_1mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_1.5mm.factor.or = sum(cliniciandata_comp$male_15mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_15mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_2mm.factor.or = sum(cliniciandata_comp$male_2mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_2mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_2.5mm.factor.or = sum(cliniciandata_comp$male_25mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_25mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_3mm.factor.or = sum(cliniciandata_comp$male_3mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_3mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_3.5mm.factor.or = sum(cliniciandata_comp$male_35mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_35mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 male_4mm.factor.or = sum(cliniciandata_comp$male_4mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$male_4mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 
								 ##Female photo
                                 female_sym.factor.or = sum(cliniciandata_comp$female_symm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="No")/length(cliniciandata_comp$female_symm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_1mm.factor.or = sum(cliniciandata_comp$female_1mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_1mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_1.5mm.factor.or = sum(cliniciandata_comp$female_15mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_15mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_2mm.factor.or = sum(cliniciandata_comp$female_2mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_2mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_2.5mm.factor.or = sum(cliniciandata_comp$female_25.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_25.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_3mm.factor.or = sum(cliniciandata_comp$female_3mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_3mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_3.5mm.factor.or = sum(cliniciandata_comp$female_35mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_35mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]),
                                 female_4mm.factor.or = sum(cliniciandata_comp$female_4mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"]=="Yes")/length(cliniciandata_comp$female_4mm.factor[cliniciandata_comp$specialty.factor!="Oral and Maxillofacial Surgery"])
								 
								 )
                                 
              
clinician_specific_response_long <- melt(clinician_specific_response)                
clinician_specific_response_long$Specialty <- c(rep("Oral and Maxillofacial Surgery", 16), rep("Orthodontist", 16))
clinician_specific_response_long$Asymmetry <- rep(c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"), 4)
clinician_specific_response_long$Asymmetry <- factor(clinician_specific_response_long$Asymmetry, levels = c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"))
clinician_specific_response_long$Image_gender <- rep(c(rep("Male", 8), rep("Female", 8)),2)
clinician_specific_response_long$Image_gender <- factor(clinician_specific_response_long$Image_gender, levels = c("Male", "Female"))


#without baseline
clinician_specific_response_long <- clinician_specific_response_long[-which(clinician_specific_response_long$Asymmetry=="Symmetric"),]

ggplot(clinician_specific_response_long, aes(x = Asymmetry, y = value, color = Specialty, group = Specialty)) +
  geom_line(size=2)+
  geom_point(size=5)+
  facet_grid(Image_gender ~ ., scales = "free", space = "free") +
  scale_color_discrete(name="Clinician Specialty", labels=c("Oral and Maxillofacial\nSurgeons", "Orthodontists"))+
  scale_y_continuous(limits=c(0,1), labels=c(0,25,50,75,100))+
  xlab("Asymmetry") +
  ylab("Percentage of Correct Response") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
	      plot.title = element_text(size=20))

```


###Students

### Proportion test for baseline

```{r}
prop.test(c(170,113),c(173,123))
prop.test(c(170,113),c(173,123), alternative = "less")
```


```{r}
student_response <- data.frame(male_sym.factor = sum(studentdata_comp$male_sym.factor=="No")/length(studentdata_comp$male_sym.factor),
                               male_1mm.factor = sum(studentdata_comp$male_1mm.factor=="Yes")/length(studentdata_comp$male_1mm.factor),
                               male_1.5mm.factor = sum(studentdata_comp$male_15mm.factor=="Yes")/length(studentdata_comp$male_15mm.factor),
                               male_2mm.factor = sum(studentdata_comp$male_2mm.factor=="Yes")/length(studentdata_comp$male_2mm.factor),
                               male_2.5mm.factor = sum(studentdata_comp$male_25mm.factor=="Yes")/length(studentdata_comp$male_25mm.factor),
                               male_3mm.factor = sum(studentdata_comp$male_3mm.factor=="Yes")/length(studentdata_comp$male_3mm.factor),
                               male_3.5mm.factor = sum(studentdata_comp$male_35mm.factor=="Yes")/length(studentdata_comp$male_35mm.factor),
                               male_4mm.factor = sum(studentdata_comp$male_4mm.factor=="Yes")/length(studentdata_comp$male_4mm.factor),
                               
                               female_sym.factor = sum(studentdata_comp$female_symm.factor=="No")/length(studentdata_comp$female_symm.factor),
                               female_1mm.factor = sum(studentdata_comp$female_1mm.factor=="Yes")/length(studentdata_comp$female_1mm.factor),
                               female_1.5mm.factor = sum(studentdata_comp$female_15mm.factor=="Yes")/length(studentdata_comp$female_15mm.factor),
                               female_2mm.factor = sum(studentdata_comp$female_2mm.factor=="Yes")/length(studentdata_comp$female_2mm.factor),
                               female_2.5mm.factor = sum(studentdata_comp$female_25.factor=="Yes")/length(studentdata_comp$female_25.factor),
                               female_3mm.factor = sum(studentdata_comp$female_3mm.factor=="Yes")/length(studentdata_comp$female_3mm.factor),
                               female_3.5mm.factor = sum(studentdata_comp$female_35mm.factor=="Yes")/length(studentdata_comp$female_35mm.factor),
                               female_4mm.factor = sum(studentdata_comp$female_4mm.factor=="Yes")/length(studentdata_comp$female_4mm.factor))
        
                
student_long <- melt(student_response)                
student_long$Respondent <- "Student"
student_long$Asymmetry <- rep(c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"), 2)
student_long$Asymmetry <- factor(student_long$Asymmetry, levels = c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"))
student_long$Image_gender <- c(rep("Male", 8), rep("Female", 8))
student_long$Image_gender <- factor(student_long$Image_gender, levels = c("Male", "Female"))


```

#### Medicine vs Pharmacy Students

```{r}
student_specific_response <- data.frame(#Medicine
							   ##Male Photo
							   male_sym.factor = sum(studentdata_comp$male_sym.factor[studentdata_comp$group.factor=="Medicine"]=="No")/length(studentdata_comp$male_sym.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_1mm.factor = sum(studentdata_comp$male_1mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_1mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_1.5mm.factor = sum(studentdata_comp$male_15mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_15mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_2mm.factor = sum(studentdata_comp$male_2mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_2mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_2.5mm.factor = sum(studentdata_comp$male_25mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_25mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_3mm.factor = sum(studentdata_comp$male_3mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_3mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_3.5mm.factor = sum(studentdata_comp$male_35mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_35mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               male_4mm.factor = sum(studentdata_comp$male_4mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$male_4mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               
							   ##Female Photo
                               female_sym.factor = sum(studentdata_comp$female_symm.factor[studentdata_comp$group.factor=="Medicine"]=="No")/length(studentdata_comp$female_symm.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_1mm.factor = sum(studentdata_comp$female_1mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_1mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_1.5mm.factor = sum(studentdata_comp$female_15mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_15mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_2mm.factor = sum(studentdata_comp$female_2mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_2mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_2.5mm.factor = sum(studentdata_comp$female_25.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_25.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_3mm.factor = sum(studentdata_comp$female_3mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_3mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_3.5mm.factor = sum(studentdata_comp$female_35mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_35mm.factor[studentdata_comp$group.factor=="Medicine"]),
                               female_4mm.factor = sum(studentdata_comp$female_4mm.factor[studentdata_comp$group.factor=="Medicine"]=="Yes")/length(studentdata_comp$female_4mm.factor[studentdata_comp$group.factor=="Medicine"]),
							   
							   #Pharmacy
							   ##Male Photo
							   male_sym.factor = sum(studentdata_comp$male_sym.factor[studentdata_comp$group.factor=="Pharmacy"]=="No")/length(studentdata_comp$male_sym.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_1mm.factor = sum(studentdata_comp$male_1mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_1mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_1.5mm.factor = sum(studentdata_comp$male_15mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_15mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_2mm.factor = sum(studentdata_comp$male_2mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_2mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_2.5mm.factor = sum(studentdata_comp$male_25mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_25mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_3mm.factor = sum(studentdata_comp$male_3mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_3mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_3.5mm.factor = sum(studentdata_comp$male_35mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_35mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               male_4mm.factor = sum(studentdata_comp$male_4mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$male_4mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               
							   ##Female Photo
                               female_sym.factor = sum(studentdata_comp$female_symm.factor[studentdata_comp$group.factor=="Pharmacy"]=="No")/length(studentdata_comp$female_symm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_1mm.factor = sum(studentdata_comp$female_1mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_1mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_1.5mm.factor = sum(studentdata_comp$female_15mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_15mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_2mm.factor = sum(studentdata_comp$female_2mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_2mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_2.5mm.factor = sum(studentdata_comp$female_25.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_25.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_3mm.factor = sum(studentdata_comp$female_3mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_3mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_3.5mm.factor = sum(studentdata_comp$female_35mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_35mm.factor[studentdata_comp$group.factor=="Pharmacy"]),
                               female_4mm.factor = sum(studentdata_comp$female_4mm.factor[studentdata_comp$group.factor=="Pharmacy"]=="Yes")/length(studentdata_comp$female_4mm.factor[studentdata_comp$group.factor=="Pharmacy"])
							   
							   )
      
student_specific_response_long <- melt(student_specific_response)                
student_specific_response_long$Specialty <- c(rep("Medicine", 16), rep("Pharmacy", 16))
student_specific_response_long$Asymmetry <- rep(c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"), 4)
student_specific_response_long$Asymmetry <- factor(student_specific_response_long$Asymmetry, levels = c("Symmetric", "1 mm", "1.5 mm", "2 mm", "2.5 mm", "3 mm", "3.5 mm", "4 mm"))
student_specific_response_long$Image_gender <- rep(c(rep("Male", 8), rep("Female", 8)),2)
student_specific_response_long$Image_gender <- factor(student_specific_response_long$Image_gender, levels = c("Male", "Female"))


#without baseline
student_specific_response_long <- student_specific_response_long[-which(student_specific_response_long$Asymmetry=="Symmetric"),]
  
ggplot(student_specific_response_long, aes(x = Asymmetry, y = value, color = Specialty, group = Specialty)) +
  geom_line(size=2)+
  geom_point(size=5)+
  facet_grid(Image_gender ~ ., scales = "free", space = "free") +
  scale_color_discrete(name="Lay Persons", labels=c("Medical Students", "Pharmacy Students"))+
  scale_y_continuous(limits=c(0,1), labels=c(0,25,50,75,100))+
  xlab("Asymmetry") +
  ylab("Percentage of Correct Response") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
	      plot.title = element_text(size=20))
```


###Combined Clinicians vs Students

```{r}
combined_long <- rbind.data.frame(clinician_long,student_long)
combined_long$Respondent <- factor(combined_long$Respondent, levels = c("Clinician", "Student"))

#without baseline
combined_long <- combined_long[-which(combined_long$Asymmetry=="Symmetric"),]

ggplot(combined_long, aes(x = Asymmetry, y = value, color = Respondent, group = Respondent)) +
  geom_line(size=2)+
  geom_point(size=5)+
  facet_grid(Image_gender ~ ., scales = "free", space = "free") +
  scale_color_discrete(name="Respondent\nClass", labels=c("Clinicians", "Lay Persons"))+
  scale_y_continuous(limits=c(0,1), labels=c(0,25,50,75,100))+
  xlab("Asymmetry") +
  ylab("Percentage of Correct Response") +
  theme_minimal() +
  theme_bw() +
  theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1
	                                 ),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        strip.text.y = element_text(size = 15),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
	      plot.title = element_text(size=20))

#unstratified
mean_long_u <- aggregate(combined_long[,2], list(combined_long$Respondent,combined_long$Asymmetry), mean)
sd_long_u <- aggregate(combined_long[,2], list(combined_long$Respondent,combined_long$Asymmetry),sd)
combined_long_u <- cbind.data.frame(mean_long_u,sd_long_u$x)

ggplot(combined_long_u, aes(x = Group.2, y = x, color = Group.1, group = Group.1)) +
    geom_line(size=1.5, position = position_dodge(.9))+
    geom_point(size=4, position=position_dodge(width = .9))+
    geom_errorbar(aes(ymin=x-sd_long_u$x, ymax=x+sd_long_u$x), position=position_dodge(width=.9))+
    scale_color_discrete(name="Respondent Class")+
    xlab("Asymmetry") +
    ylab("Probability of Correct Response") +
    theme_minimal() +
    theme_bw() +
    theme(axis.text.x = element_text(size=15,
                                     angle = 45, 
                                     #margin = ggplot2::margin(t = 35),
                                     hjust = 1
    ),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20),
    legend.text=element_text(size=15),
    legend.title=element_text(size=20),
    plot.title = element_text(size=20))
```

