---
title: "Repeated Measures Logistic Regression"
author: "Spiro Stilianoudakis"
date: "April 26, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading Packages

```{r}
library(dplyr)
library(lme4)
library(car)
```

# Set working directory

```{r}
setwd("X:/CommonPrograms/Oral Health Services Research Core/Spiro/Asymmetry")
```


# Reading in stacked dataset

```{r}
asymmetry <- readRDS("stacked_all.rds")
asymmetry$correct <- relevel(asymmetry$correct, ref = 1)

#continuous repeated measures variable
asymmetry$asymmetry_cont <- as.numeric(gsub("mm","",asymmetry$asymmetry))
  
#attach(asymmetry)
```

# Frequency tables

## Ignoring image gender

```{r}
#sample sizes
table(asymmetry$respondent_group,asymmetry$asymmetry,asymmetry$gender_photo)

#table of responses (ignoring gender of photo)
table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)

#column percentages across each repeated measure (ignoring gender of photo)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,1],2)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,2],2)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,3],2)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,4],2)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,5],2)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,6],2)
prop.table(table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)[,,7],2)

#percentage of correct responses (ignoring gender of photo)
tab1 <- table(asymmetry$correct, asymmetry$respondent_group, asymmetry$asymmetry)
propcorrect1mm <- prop.table(tab1[,,1],2)
propcorrect1.5mm <- prop.table(tab1[,,2],2)
propcorrect2mm <- prop.table(tab1[,,3],2)
propcorrect2.5mm <- prop.table(tab1[,,4],2)
propcorrect3mm <- prop.table(tab1[,,5],2)
propcorrect3.5mm <- prop.table(tab1[,,6],2)
propcorrect4mm <- prop.table(tab1[,,7],2)

PercentageCorrect <- rbind(propcorrect1mm[2,],
                           propcorrect1.5mm[2,],
                           propcorrect2mm[2,],
                           propcorrect2.5mm[2,],
                           propcorrect3mm[2,],
                           propcorrect3.5mm[2,],
                           propcorrect4mm[2,])
PercentageCorrect <- rbind(cbind(c(table(cliniciandata_comp$male_sym.factor)[2]+table(cliniciandata_comp$female_symm.factor)[2])/sum(table(cliniciandata_comp$male_sym.factor)+table(cliniciandata_comp$female_symm.factor)),c(table(studentdata_comp$male_sym.factor)[2]+table(studentdata_comp$female_symm.factor)[2])/sum(table(studentdata_comp$male_sym.factor)+table(studentdata_comp$female_symm.factor))),
                           PercentageCorrect)
rownames(PercentageCorrect) <- c("Symmetric", "1mm", "1.5mm", "2mm", "2.5mm", "3mm", "3.5mm", "4mm")
```

## With image gender

### Male

```{r}
asymmetry_male <- asymmetry[which(asymmetry$gender_photo=="Male"),]

#table of responses (ignoring gender of photo)
table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)

#column percentages across each repeated measure (ignoring gender of photo)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,1],2)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,2],2)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,3],2)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,4],2)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,5],2)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,6],2)
prop.table(table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)[,,7],2)

#percentage of correct responses (ignoring gender of photo)
tab1 <- table(asymmetry_male$correct, asymmetry_male$respondent_group, asymmetry_male$asymmetry)
propcorrect1mm <- prop.table(tab1[,,1],2)
propcorrect1.5mm <- prop.table(tab1[,,2],2)
propcorrect2mm <- prop.table(tab1[,,3],2)
propcorrect2.5mm <- prop.table(tab1[,,4],2)
propcorrect3mm <- prop.table(tab1[,,5],2)
propcorrect3.5mm <- prop.table(tab1[,,6],2)
propcorrect4mm <- prop.table(tab1[,,7],2)

PercentageCorrect_male <- rbind(propcorrect1mm[2,],
                           propcorrect1.5mm[2,],
                           propcorrect2mm[2,],
                           propcorrect2.5mm[2,],
                           propcorrect3mm[2,],
                           propcorrect3.5mm[2,],
                           propcorrect4mm[2,])

PercentageCorrect_male <- rbind(cbind(table(cliniciandata_comp$male_sym.factor)[2]/sum(table(cliniciandata_comp$male_sym.factor)),c(table(studentdata_comp$male_sym.factor)[2])/sum(table(studentdata_comp$male_sym.factor))),
                           PercentageCorrect_male)
rownames(PercentageCorrect_male) <- c("Symmetric", "1mm", "1.5mm", "2mm", "2.5mm", "3mm", "3.5mm", "4mm")
```

### Female

```{r}
asymmetry_female <- asymmetry[which(asymmetry$gender_photo=="Female"),]

#table of responses (ignoring gender of photo)
table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)

#column percentages across each repeated measure (ignoring gender of photo)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,1],2)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,2],2)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,3],2)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,4],2)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,5],2)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,6],2)
prop.table(table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)[,,7],2)

#percentage of correct responses (ignoring gender of photo)
tab1 <- table(asymmetry_female$correct, asymmetry_female$respondent_group, asymmetry_female$asymmetry)
propcorrect1mm <- prop.table(tab1[,,1],2)
propcorrect1.5mm <- prop.table(tab1[,,2],2)
propcorrect2mm <- prop.table(tab1[,,3],2)
propcorrect2.5mm <- prop.table(tab1[,,4],2)
propcorrect3mm <- prop.table(tab1[,,5],2)
propcorrect3.5mm <- prop.table(tab1[,,6],2)
propcorrect4mm <- prop.table(tab1[,,7],2)

PercentageCorrect_female <- rbind(propcorrect1mm[2,],
                           propcorrect1.5mm[2,],
                           propcorrect2mm[2,],
                           propcorrect2.5mm[2,],
                           propcorrect3mm[2,],
                           propcorrect3.5mm[2,],
                           propcorrect4mm[2,])

PercentageCorrect_female <- rbind(cbind(table(cliniciandata_comp$female_symm.factor)[2]/sum(table(cliniciandata_comp$female_symm.factor)),c(table(studentdata_comp$female_symm.factor)[2])/sum(table(studentdata_comp$female_symm.factor))),
                           PercentageCorrect_female)
rownames(PercentageCorrect_female) <- c("Symmetric", "1mm", "1.5mm", "2mm", "2.5mm", "3mm", "3.5mm", "4mm")
```


# Setting contrasts for factors

```{r}
#contrasts(asymmetry$respondent_group) <- contr.sum(2)
#contrasts(asymmetry$asymmetry) <- contr.sum(7)
```

# Naive logistic regression, ignoring repeated measures, ignoring gender of photo
 
```{r}
#with interaction
naiveglm = glm(correct ~ respondent_group*asymmetry,
               data=asymmetry,
               family=binomial)
summary(naiveglm)

#no interaction
naiveglm2 = glm(correct ~ respondent_group+asymmetry,
               data=asymmetry,
               family=binomial)
summary(naiveglm2)
```

## Likelihood ratio tests

```{r}
anova(naiveglm, test="Chisq") # Terms added sequentially first to last
Anova(naiveglm, type="III") # Each term is last

anova(naiveglm2, test="Chisq") # Terms added sequentially first to last
Anova(naiveglm2, type="III") # Each term is last
```

# Fit a mixed model; random intercept

## Image Gender: Male

```{r}
asymmetry.male <- asymmetry[which(asymmetry$gender_photo=="Male"),]
asymmetry.male <- asymmetry.male[,c(1,2,4,5)]

asymm.male.mixed1 = glmer(correct ~ respondent_group*asymmetry + (1 | ID), 
              data=asymmetry.male,
              family=binomial(link = "logit"),
              #correlation = corAR1(form = ~ 1 | ID), cant set correlation structure
              glmerControl(optimizer = "bobyqa"),
              nAGQ = 10)

Anova(asymm.male.mixed1, type="III")

#final model
asymm.male.mixed.f = asymm.male.mixed1

summary(asymm.male.mixed.f)

#confidence intervals
se <- sqrt(diag(vcov(asymm.male.mixed.f)))
# table of estimates with 95% CI
tab <- cbind(Est = fixef(asymm.male.mixed.f), LL = fixef(asymm.male.mixed.f) - 1.96 * se, UL = fixef(asymm.male.mixed.f) + 1.96 *
    se)

round(exp(tab),4)

#plotting
jvalues <- c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm")
tmpdat <- asymmetry.male
pp <- lapply(jvalues, function(j) {
    tmpdat$asymmetry <- j
    predict(asymm.male.mixed.f, newdata = tmpdat, type = "response")
})
sapply(pp[c(1:7)], median)
plotdat <- t(sapply(pp, function(x) {
    c(M = median(x), quantile(x, c(0.25, 0.75)))
}))
plotdat <- cbind.data.frame(plotdat, jvalues)
plotdat$jvalues <- factor(plotdat$jvalues, levels=c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm"))


# better names and show the first few rows
colnames(plotdat) <- c("PredictedProbability", "Lower", "Upper", "Asymmetry")
head(plotdat)
ggplot(plotdat, aes(x = Asymmetry, y = PredictedProbability, group = 1)) + geom_line() + geom_point() +
    ylim(c(0, 1))
ggplot(plotdat, aes(x = Asymmetry, y = PredictedProbability, group = 1)) + geom_linerange(aes(ymin = Lower,
    ymax = Upper)) + geom_line() + geom_point() + ylim(c(0, 1))

# calculate predicted probabilities and store in a list
biprobs <- lapply(levels(asymmetry.male$respondent_group), function(grp) {
  tmpdat$respondent_group[] <- grp
  lapply(jvalues, function(j) {
    tmpdat$asymmetry <- j
    predict(asymm.male.mixed.f, newdata = tmpdat, type = "response")
  })
})

# get means and quartiles for all jvalues for each level of group
plotdat2 <- lapply(biprobs, function(X) {
  temp <- t(sapply(X, function(x) {
    c(M=median(x), quantile(x, c(.25, .75)))
  }))
  temp <- as.data.frame(cbind(temp, jvalues))
  colnames(temp) <- c("PredictedProbability", "Lower", "Upper", "Asymmetry")
  return(temp)
})

# collapse to one data frame
plotdat2 <- do.call(rbind, plotdat2)

# add group
plotdat2$Respondent <- factor(rep(levels(asymmetry.male$respondent_group), each = length(jvalues)))

# show first few rows
plotdat2$PredictedProbability <- as.numeric(as.character(plotdat2$PredictedProbability))
plotdat2$Lower <- as.numeric(as.character(plotdat2$Lower))
plotdat2$Upper <- as.numeric(as.character(plotdat2$Upper))
plotdat2$Asymmetry <- factor(plotdat2$Asymmetry,levels=c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm"))
head(plotdat2)

ggplot(plotdat2, aes(x = Asymmetry, y = PredictedProbability, group=Respondent)) +
  geom_ribbon(aes(ymin = Lower, ymax = Upper, fill = Respondent), alpha = .15) +
  geom_line(aes(colour = Respondent), size = 1) + geom_point(aes(colour = Respondent), size = 2) +
  ylim(c(0, 1)) 


```

### Agregating Results

```{r}
# Make a table of estimated population mean log odds
X = model.matrix(asymm.male.mixed.f) # The X matrix!
summod = summary(asymm.male.mixed.f)
betahat = cbind(summod$coef[,1]) # Estimated fixed effects as a column vector.
estlogodds = X %*% betahat # Estimated pop mean log odds for each observation.

aggmeans = aggregate(estlogodds, by = list(asymmetry.male$respondent_group,asymmetry.male$asymmetry), FUN = mean)
aggmeans

treatmeans = aggmeans[,3]
dim(treatmeans) = c(2,7)

rownames(treatmeans) = c("Clinician", "Student")
colnames(treatmeans) = c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm")
round(addmargins(treatmeans,FUN=mean, quiet=T),2) # With marginal means

```

### Testing differences between Clinicians and Students at each asymmetry

```{r}

# Test pairwise differences between marginal means with a Bonferroni correction
##
n = length(asymmetry.male$ID); n
 
respondentcond <- character(n) 
for(j in 1:n) respondentcond[j] = paste(asymmetry.male$respondent_group[j],asymmetry.male$asymmetry[j],sep='')
freq = table(respondentcond); freq

# Fit a no-intercept model on the combination variable. 
asymmetry.male$respondentcond <- respondentcond
asymmetry.male$respondentcond <- factor(asymmetry.male$respondentcond, levels=c("Clinician1mm",
         "Clinician1.5mm",
         "Clinician2mm",
         "Clinician2.5mm",
         "Clinician3mm",
         "Clinician3.5mm",
         "Clinician4mm",
         "Student1mm",
         "Student1.5mm",
         "Student2mm",
         "Student2.5mm",
         "Student3mm",
         "Student3.5mm",
         "Student4mm"))
noint = glmer(correct ~ 0 + respondentcond + (1 | ID),
              data=asymmetry.male,
              family=binomial(link = "logit"),
              #correlation = corAR1(form = ~ 1 | ID), cant set correlation structure
              glmerControl(optimizer = "bobyqa"),
              nAGQ = 10) 

nointsum = summary(noint); nointsum

comparing_respondents_mat = rbind(
+ # 1             2             3            4              5             6             7            8           9           10         11           12          13           14  
+ # Clinician1mm Clinician1.5mm Clinician2mm Clinician2.5mm Clinician3mm Clinician3.5mm Clinician4mm Student1mm Student1.5mm Student2mm Student2.5mm Student3mm Student3.5mm Student4mm
+ #  1  2  3   4  5  6  7  8  9  10  11  12 13  14
+ c( 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0),
+ c( 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0),
+ c( 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0),
+ c( 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0),
+ c( 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0),
+ c( 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0),
+ c( 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1))

colnames(comparing_respondents_mat) = levels(asymmetry.male$respondentcond)
rownames(comparing_respondents_mat) = c("CvS:1mm", "CvS:1.5mm", "CvS:2mm", "CvS:2.5mm", "CvS:3mm", "CvS:3.5mm", "CvS:4mm")

# Make pairwise comparison matrices. Chi-squared test statistics will be in the
# upper triangle, and unadjusted p-values in the lower triangle.
Pairwise1 = cbind(rep(0,7),rep(0,7))
colnames(Pairwise1) = c("Test Statistic", "P-Value")

for(i in 1:7){

 L = comparing_respondents_mat[i,]
 Ltest = linearHypothesis(noint,L) # Testing H0: L beta = 0
 Pairwise1[i,1] = Ltest[2,2] # Test statistic
 Pairwise1[i,2] = Ltest[2,3] # p-value
} 
Pairwise1[,1] <- round(Pairwise1[,1], 2)
Pairwise1[,2] <- round(Pairwise1[,2], 5)
Pairwise1 <- as.data.frame(Pairwise1)
Pairwise1$PValue.Adjust <- p.adjust(Pairwise1[,2], method = "bonferroni")
```

### Testing differences between consecutive asymmetries

```{r}
comparing_asymmetries_mat = rbind(
+ # 1             2             3            4              5             6             7            8           9           10         11           12          13           14  
+ # Clinician1mm Clinician1.5mm Clinician2mm Clinician2.5mm Clinician3mm Clinician3.5mm Clinician4mm Student1mm Student1.5mm Student2mm Student2.5mm Student3mm Student3.5mm Student4mm
+ #  1  2  3   4  5  6  7  8  9  10  11  12 13  14
+ c( 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1))

colnames(comparing_asymmetries_mat) = levels(asymmetry.male$respondentcond)
rownames(comparing_asymmetries_mat) = c("1mmv1.5mm:C",
                                         "1.5mmv2mm:C",
                                         "2mmv2.5mm:C",
                                         "2.5mmv3mm:C",
                                         "3mmv3.5mm:C",
                                         "3.5mmv4mm:C",
                                         "1mmv1.5mm:S",
                                         "1.5mmv2mm:S",
                                         "2mmv2.5mm:S",
                                         "2.5mmv3mm:S",
                                         "3mmv3.5mm:S",
                                         "3.5mmv4mm:S")

# Make pairwise comparison matrices. Chi-squared test statistics will be in the
# upper triangle, and unadjusted p-values in the lower triangle.
Pairwise2 = cbind(rep(0,12),rep(0,12))
colnames(Pairwise2) = c("Test Statistic", "PValue")

for(i in 1:12){

 L = comparing_asymmetries_mat[i,]
 Ltest = linearHypothesis(noint,L) # Testing H0: L beta = 0
 Pairwise2[i,1] = Ltest[2,2] # Test statistic
 Pairwise2[i,2] = Ltest[2,3] # p-value
} 
Pairwise2[,1] <- round(Pairwise2[,1], 2)
Pairwise2[,2] <- round(Pairwise2[,2], 5)
Pairwise2 <- as.data.frame(Pairwise2)
Pairwise2$PValue.Adjust <- p.adjust(Pairwise2[,2], method = "bonferroni")
```

### Testing differences of differences between consecutive asymmetries between clinicians and students

```{r}
comparing_asymmetries_mat2 = rbind(
+ # 1             2             3            4              5             6             7            8           9           10         11           12          13           14  
+ # Clinician1mm Clinician1.5mm Clinician2mm Clinician2.5mm Clinician3mm Clinician3.5mm Clinician4mm Student1mm Student1.5mm Student2mm Student2.5mm Student3mm Student3.5mm Student4mm
+ #  1  2  3   4  5  6  7  8  9  10  11  12 13  14
+ c( 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
+ c( 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0),
+ c( 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0),
+ c( 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0),
+ c( 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0),
+ c( 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1))

colnames(comparing_asymmetries_mat2) = levels(asymmetry.male$respondentcond)
rownames(comparing_asymmetries_mat2) = c("1mmv1.5mm;C:1mmv1.5mm;S",
                                        "1.5mmv2mm;C:1.5mmv2mm;S",
                                        "2mmv2.5mm;C:2mmv2.5mm;S",
                                        "2.5mmv3mm;C:2.5mmv3mm;S",
                                        "3mmv3.5mm;C:3mmv3.5mm;S",
                                        "3.5mmv4mm;C:3.5mmv4mm;S")

# Make pairwise comparison matrices. Chi-squared test statistics will be in the
# upper triangle, and unadjusted p-values in the lower triangle.
Pairwise3 = cbind(rep(0,6),rep(0,6))
colnames(Pairwise3) = c("Test Statistic", "PValue")

for(i in 1:6){

 L = comparing_asymmetries_mat2[i,]
 Ltest = linearHypothesis(noint,L) # Testing H0: L beta = 0
 Pairwise3[i,1] = Ltest[2,2] # Test statistic
 Pairwise3[i,2] = Ltest[2,3] # p-value
} 
Pairwise3[,1] <- round(Pairwise3[,1], 2)
Pairwise3[,2] <- round(Pairwise3[,2], 5)
Pairwise3 <- as.data.frame(Pairwise3)
Pairwise3$PValue.Adjust <- p.adjust(Pairwise3[,2], method = "bonferroni")
```

## Image Gender: Female

```{r}
asymmetry.Female <- asymmetry[which(asymmetry$gender_photo=="Female"),]
asymmetry.Female <- asymmetry.Female[,c(1,2,4,5)]

asymm.Female.mixed1 = glmer(correct ~ respondent_group*asymmetry + (1 | ID), 
              data=asymmetry.Female,
              family=binomial(link = "logit"),
              #correlation = corAR1(form = ~ 1 | ID), cant set correlation structure
              glmerControl(optimizer = "bobyqa"),
              nAGQ = 10)

Anova(asymm.Female.mixed1, type="III")

#final model
asymm.Female.mixed.f = asymm.Female.mixed1

summary(asymm.Female.mixed.f)

#confidence intervals
se <- sqrt(diag(vcov(asymm.Female.mixed.f)))
# table of estimates with 95% CI
tab <- cbind(Est = fixef(asymm.Female.mixed.f), LL = fixef(asymm.Female.mixed.f) - 1.96 * se, UL = fixef(asymm.Female.mixed.f) + 1.96 *
    se)

round(exp(tab),4)

#plotting
jvalues <- c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm")
tmpdat <- asymmetry.Female
pp <- lapply(jvalues, function(j) {
    tmpdat$asymmetry <- j
    predict(asymm.Female.mixed.f, newdata = tmpdat, type = "response")
})
sapply(pp[c(1:7)], median)
plotdat <- t(sapply(pp, function(x) {
    c(M = median(x), quantile(x, c(0.25, 0.75)))
}))
plotdat <- cbind.data.frame(plotdat, jvalues)
plotdat$jvalues <- factor(plotdat$jvalues, levels=c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm"))


# better names and show the first few rows
colnames(plotdat) <- c("PredictedProbability", "Lower", "Upper", "Asymmetry")
head(plotdat)
ggplot(plotdat, aes(x = Asymmetry, y = PredictedProbability, group = 1)) + geom_line() + geom_point() +
    ylim(c(0, 1))
ggplot(plotdat, aes(x = Asymmetry, y = PredictedProbability, group = 1)) + geom_linerange(aes(ymin = Lower,
    ymax = Upper)) + geom_line() + geom_point() + ylim(c(0, 1))

# calculate predicted probabilities and store in a list
biprobs <- lapply(levels(asymmetry.Female$respondent_group), function(grp) {
  tmpdat$respondent_group[] <- grp
  lapply(jvalues, function(j) {
    tmpdat$asymmetry <- j
    predict(asymm.Female.mixed.f, newdata = tmpdat, type = "response")
  })
})

# get means and quartiles for all jvalues for each level of group
plotdat2 <- lapply(biprobs, function(X) {
  temp <- t(sapply(X, function(x) {
    c(M=median(x), quantile(x, c(.25, .75)))
  }))
  temp <- as.data.frame(cbind(temp, jvalues))
  colnames(temp) <- c("PredictedProbability", "Lower", "Upper", "Asymmetry")
  return(temp)
})

# collapse to one data frame
plotdat2 <- do.call(rbind, plotdat2)

# add group
plotdat2$Respondent <- factor(rep(levels(asymmetry.Female$respondent_group), each = length(jvalues)))

# show first few rows
plotdat2$PredictedProbability <- as.numeric(as.character(plotdat2$PredictedProbability))
plotdat2$Lower <- as.numeric(as.character(plotdat2$Lower))
plotdat2$Upper <- as.numeric(as.character(plotdat2$Upper))
plotdat2$Asymmetry <- factor(plotdat2$Asymmetry,levels=c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm"))
head(plotdat2)

ggplot(plotdat2, aes(x = Asymmetry, y = PredictedProbability, group=Respondent)) +
  geom_ribbon(aes(ymin = Lower, ymax = Upper, fill = Respondent), alpha = .15) +
  geom_line(aes(colour = Respondent), size = 1) + geom_point(aes(colour = Respondent), size = 2) +
  ylim(c(0, 1)) 


```

### Agregating Results

```{r}
# Make a table of estimated population mean log odds
X = model.matrix(asymm.Female.mixed.f) # The X matrix!
summod = summary(asymm.Female.mixed.f)
betahat = cbind(summod$coef[,1]) # Estimated fixed effects as a column vector.
estlogodds = X %*% betahat # Estimated pop mean log odds for each observation.

aggmeans = aggregate(estlogodds, by = list(asymmetry.Female$respondent_group,asymmetry.Female$asymmetry), FUN = mean)
aggmeans

treatmeans = aggmeans[,3]
dim(treatmeans) = c(2,7)

rownames(treatmeans) = c("Clinician", "Student")
colnames(treatmeans) = c("1mm","1.5mm","2mm","2.5mm","3mm","3.5mm","4mm")
round(addmargins(treatmeans,FUN=mean, quiet=T),2) # With marginal means

```

### Testing differences between Clinicians and Students at each asymmetry

```{r}

# Test pairwise differences between marginal means with a Bonferroni correction
##
n = length(asymmetry.Female$ID); n
 
respondentcond <- character(n) 
for(j in 1:n) respondentcond[j] = paste(asymmetry.Female$respondent_group[j],asymmetry.Female$asymmetry[j],sep='')
freq = table(respondentcond); freq

# Fit a no-intercept model on the combination variable. 
asymmetry.Female$respondentcond <- respondentcond
asymmetry.Female$respondentcond <- factor(asymmetry.Female$respondentcond, levels=c("Clinician1mm",
         "Clinician1.5mm",
         "Clinician2mm",
         "Clinician2.5mm",
         "Clinician3mm",
         "Clinician3.5mm",
         "Clinician4mm",
         "Student1mm",
         "Student1.5mm",
         "Student2mm",
         "Student2.5mm",
         "Student3mm",
         "Student3.5mm",
         "Student4mm"))
noint = glmer(correct ~ 0 + respondentcond + (1 | ID),
              data=asymmetry.Female,
              family=binomial(link = "logit"),
              #correlation = corAR1(form = ~ 1 | ID), cant set correlation structure
              glmerControl(optimizer = "bobyqa"),
              nAGQ = 10) 

nointsum = summary(noint); nointsum

comparing_respondents_mat = rbind(
+ # 1             2             3            4              5             6             7            8           9           10         11           12          13           14  
+ # Clinician1mm Clinician1.5mm Clinician2mm Clinician2.5mm Clinician3mm Clinician3.5mm Clinician4mm Student1mm Student1.5mm Student2mm Student2.5mm Student3mm Student3.5mm Student4mm
+ #  1  2  3   4  5  6  7  8  9  10  11  12 13  14
+ c( 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0, 0),
+ c( 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0, 0),
+ c( 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0, 0),
+ c( 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0, 0),
+ c( 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0, 0),
+ c( 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1, 0),
+ c( 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, -1))

colnames(comparing_respondents_mat) = levels(asymmetry.Female$respondentcond)
rownames(comparing_respondents_mat) = c("CvS:1mm", "CvS:1.5mm", "CvS:2mm", "CvS:2.5mm", "CvS:3mm", "CvS:3.5mm", "CvS:4mm")

# Make pairwise comparison matrices. Chi-squared test statistics will be in the
# upper triangle, and unadjusted p-values in the lower triangle.
Pairwise1 = cbind(rep(0,7),rep(0,7))
colnames(Pairwise1) = c("Test Statistic", "P-Value")

for(i in 1:7){

 L = comparing_respondents_mat[i,]
 Ltest = linearHypothesis(noint,L) # Testing H0: L beta = 0
 Pairwise1[i,1] = Ltest[2,2] # Test statistic
 Pairwise1[i,2] = Ltest[2,3] # p-value
} 
Pairwise1[,1] <- round(Pairwise1[,1], 2)
Pairwise1[,2] <- round(Pairwise1[,2], 5)
Pairwise1 <- as.data.frame(Pairwise1)
Pairwise1$PValue.Adjust <- p.adjust(Pairwise1[,2], method = "bonferroni")
```

### Testing differences between consecutive asymmetries

```{r}
comparing_asymmetries_mat = rbind(
+ # 1             2             3            4              5             6             7            8           9           10         11           12          13           14  
+ # Clinician1mm Clinician1.5mm Clinician2mm Clinician2.5mm Clinician3mm Clinician3.5mm Clinician4mm Student1mm Student1.5mm Student2mm Student2.5mm Student3mm Student3.5mm Student4mm
+ #  1  2  3   4  5  6  7  8  9  10  11  12 13  14
+ c( 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1, 0),
+ c( 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, -1))

colnames(comparing_asymmetries_mat) = levels(asymmetry.Female$respondentcond)
rownames(comparing_asymmetries_mat) = c("1mmv1.5mm:C",
                                         "1.5mmv2mm:C",
                                         "2mmv2.5mm:C",
                                         "2.5mmv3mm:C",
                                         "3mmv3.5mm:C",
                                         "3.5mmv4mm:C",
                                         "1mmv1.5mm:S",
                                         "1.5mmv2mm:S",
                                         "2mmv2.5mm:S",
                                         "2.5mmv3mm:S",
                                         "3mmv3.5mm:S",
                                         "3.5mmv4mm:S")

# Make pairwise comparison matrices. Chi-squared test statistics will be in the
# upper triangle, and unadjusted p-values in the lower triangle.
Pairwise2 = cbind(rep(0,12),rep(0,12))
colnames(Pairwise2) = c("Test Statistic", "PValue")

for(i in 1:12){

 L = comparing_asymmetries_mat[i,]
 Ltest = linearHypothesis(noint,L) # Testing H0: L beta = 0
 Pairwise2[i,1] = Ltest[2,2] # Test statistic
 Pairwise2[i,2] = Ltest[2,3] # p-value
} 
Pairwise2[,1] <- round(Pairwise2[,1], 2)
Pairwise2[,2] <- round(Pairwise2[,2], 5)
Pairwise2 <- as.data.frame(Pairwise2)
Pairwise2$PValue.Adjust <- p.adjust(Pairwise2[,2], method = "bonferroni")
```

### Testing differences of differences between consecutive asymmetries between clinicians and students

```{r}
comparing_asymmetries_mat2 = rbind(
+ # 1             2             3            4              5             6             7            8           9           10         11           12          13           14  
+ # Clinician1mm Clinician1.5mm Clinician2mm Clinician2.5mm Clinician3mm Clinician3.5mm Clinician4mm Student1mm Student1.5mm Student2mm Student2.5mm Student3mm Student3.5mm Student4mm
+ #  1  2  3   4  5  6  7  8  9  10  11  12 13  14
+ c( 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0),
+ c( 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0),
+ c( 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0, 0),
+ c( 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0, 0),
+ c( 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1, 0),
+ c( 0, 0, 0, 0, 0, 1, -1, 0, 0, 0, 0, 0, 1, -1))

colnames(comparing_asymmetries_mat2) = levels(asymmetry.Female$respondentcond)
rownames(comparing_asymmetries_mat2) = c("1mmv1.5mm;C:1mmv1.5mm;S",
                                        "1.5mmv2mm;C:1.5mmv2mm;S",
                                        "2mmv2.5mm;C:2mmv2.5mm;S",
                                        "2.5mmv3mm;C:2.5mmv3mm;S",
                                        "3mmv3.5mm;C:3mmv3.5mm;S",
                                        "3.5mmv4mm;C:3.5mmv4mm;S")

# Make pairwise comparison matrices. Chi-squared test statistics will be in the
# upper triangle, and unadjusted p-values in the lower triangle.
Pairwise3 = cbind(rep(0,6),rep(0,6))
colnames(Pairwise3) = c("Test Statistic", "PValue")

for(i in 1:6){

 L = comparing_asymmetries_mat2[i,]
 Ltest = linearHypothesis(noint,L) # Testing H0: L beta = 0
 Pairwise3[i,1] = Ltest[2,2] # Test statistic
 Pairwise3[i,2] = Ltest[2,3] # p-value
} 
Pairwise3[,1] <- round(Pairwise3[,1], 2)
Pairwise3[,2] <- round(Pairwise3[,2], 5)
Pairwise3 <- as.data.frame(Pairwise3)
Pairwise3$PValue.Adjust <- p.adjust(Pairwise3[,2], method = "bonferroni")
```
